What We Eval in the Shadows

### 2021-08-13 paper/main.tex
Some fixes on Section 7

The cases where \eval appears to be overkill include simple expression shapes
such as \k{X}, \k{V}, \k{\$}, \k{<-}, and \k{FUN}. Variable lookup in a remote
environment can be performed by the builtin \k{get} function, a similar case
can be made for assignment and the \k{assign} function. There is a dedicated
\k{do.call} function to build function calls. However, the unnecessary uses of
\eval often can only be uncovered by manual analysis.

@@

For example in Listing~\ref{lst:unnecessary}, the function uses \eval to lookup
a target function name from a constructed string. Then it constructs a calls it
with the arguments that are passed to the current function. \Eval is overkill
in this case, a semantically equivalent function body uses \k{get} to perform
the lookup and then calls the resulting function directly.

@@

% TODO: remove - does not bring anything new or interesting
As a last example, \k{configr::config.funs.par} construct three expressions
that are then fed to \eval. Semantically equivalent code would use \k{get}
to lookup \k{fun}, and then directly execute the three expressions.

>>>>

The cases where \eval appears to be overkill include simple expression shapes
such as \k{X}, \k{V}, \k{\$}, \k{<-}, and \k{FUN}. Variable lookup in a remote
environment can be performed by the builtin \k{get} function, a similar case
can be made for assignment and the \k{assign} function. There is a dedicated
\k{do.call} function to perform function calls. However, the unnecessary uses of
\eval often can only be uncovered by manual analysis.

@@

For example in Listing~\ref{lst:unnecessary}, the function uses \eval to lookup
a target function name from a constructed string. Then it constructs a calls it
with the arguments that are passed to the current function. \Eval is overkill
in this case: a semantically equivalent function body can use \k{get} to perform
the lookup and then call the resulting function directly.

@@

% TODO: remove - does not bring anything new or interesting
As a last example, \k{configr::config.funs.par} constructs three expressions
that are then fed to \eval. Semantically equivalent code would use \k{get}
to lookup \k{fun}, and then directly execute the three expressions.
